Squintability and Other Metrics for Assessing Projection Pursuit Indexes, and Guiding Optimisation Choices

### 2025-03-01 jso.qmd
model fits all in same chunk

mod1 <- glm(proportion ~ smoothness + squintability + d + n_jellies + max_tries, data = sim_df2, family = binomial) 
```

@@

```{r}
#| tbl-pos: H
#| label: tbl-joint-output
library(kableExtra)
mod2 <- glm(proportion ~ squintability + d + n_jellies + max_tries, data = sim_df2, family = binomial)
mod3 <- glm(proportion ~ smoothness + d + n_jellies + max_tries, data = sim_df2, family = binomial)
summary_table <- bind_rows(
  glance(mod2) %>% mutate(Model = "Squintability"),
  glance(mod3) %>% mutate(Model = "Smoothness")
) %>%
  select(Model, null.deviance, df.null, logLik, df.residual, AIC, BIC) %>%
  rename(
    `Null Deviance` = null.deviance,
    `DF Null` = df.null,
    `Log-Likelihood` = logLik,
    `DF Residual` = df.residual
  ) %>%
  mutate(across(where(is.numeric), ~ round(.x, 2)))
summary_table %>%
  kable(caption = "Model summaries for squintability and smoothness separately") %>%
  kable_styling(font_size = 10) %>%
  column_spec(1, bold = TRUE, width = "5em")
```

>>>>

mod1 <- glm(proportion ~ smoothness + squintability + d + n_jellies + max_tries, data = sim_df2, family = binomial) 
mod2 <- glm(proportion ~ squintability + d + n_jellies + max_tries, data = sim_df2, family = quasibinomial)
mod3 <- glm(proportion ~ smoothness + d + n_jellies + max_tries, data = sim_df2, family = quasibinomial)
mod4 <- glm(proportion ~ squintability*d + n_jellies, data = sim_df2, family = quasibinomial)
```

@@

```{r}
#| tbl-pos: H
#| label: tbl-joint-output
library(kableExtra)
summary_table <- bind_rows(
  glance(mod1) %>% mutate(Model = "Full"),
  #glance(mod2) %>% mutate(Model = "Squintability"),
  #glance(mod3) %>% mutate(Model = "Smoothness")
  glance(mod4) %>% mutate(Model = "Interaction")
) |>
  select(Model, deviance, df.residual, null.deviance, df.null, #logLik, 
         ) |> #, AIC, BIC) %>%
  rename(
    `Null Deviance` = null.deviance,
    `DF Null` = df.null,
    `Deviance` = deviance,
    `DF Residual` = df.residual#,
    #`Log-Likelihood` = logLik,
  ) |>
  mutate(across(where(is.numeric), ~ round(.x, 2)))
summary_table |>
  kable(caption = "Fit statistics for models: full, individual squintability and smoothness. The full model (and the model containing squintability but not smoothness) explains more than 50% of the variability in optimisation success.") |>
  kable_styling(font_size = 10) |>
  row_spec(0, bold = TRUE) #, width = "5em")
```

### 2025-03-01 jso.tex
model fits all in same chunk

\begin{tcolorbox}[enhanced jigsaw, opacitybacktitle=0.6, colback=white, arc=.35mm, coltitle=black, leftrule=.75mm, opacityback=0, colframe=quarto-callout-note-color-frame, breakable, toptitle=1mm, bottomtitle=1mm, colbacktitle=quarto-callout-note-color!10!white, toprule=.15mm, title={Algorithm: Jellyfish Optimizer Pseudo Code}, titlerule=0mm, left=2mm, bottomrule=.15mm, rightrule=.15mm]

>>>>

\begin{tcolorbox}[enhanced jigsaw, rightrule=.15mm, toprule=.15mm, breakable, colbacktitle=quarto-callout-note-color!10!white, titlerule=0mm, colframe=quarto-callout-note-color-frame, left=2mm, bottomtitle=1mm, bottomrule=.15mm, toptitle=1mm, opacityback=0, colback=white, title={Algorithm: Jellyfish Optimizer Pseudo Code}, opacitybacktitle=0.6, leftrule=.75mm, arc=.35mm, coltitle=black]
